\documentclass[11pt,a4paper]{article}

\input{format}

\begin{document}

\title{Quasars in Crisis: Grumpy Question}
\maketitle


\section*{Accretion}
\begin{itemize}
\item What is the origin of the soft X-ray excess/UV downturn? 
\item Why do disks look different at 0.2$L_{\rm Edd}$ in AGN (big Soft X-ray excess/UV downturn) than in Binaries (something that looks and varies like a Shakura-Sunyaev disc!) 
\item At around eddington the NLS1 do look like a disc - but why are there discs in AGN when 
they are radiation pressure unstable?
\item Why are there discs in  black hole binaries since they are radiation pressure unstable too (just not quite so badly as AGN!)
\item How do we make discs vary - the NLS1 have optical/UV that change on timescales of weeks-months yet this can't be reprocessing as the x-rays are weak.
\item How badly has Cloudy misled the AGN field?
\item Do {\it any} supermassive black holes accrete super-critically?
\item Is Soltan wrong?  Are we missing *significant* accretion in the Universe?
        (we just don’t see TDEs in $\log M_{\rm BH}/M_{\odot} > 7.5$ objects; 
 Andrew King’s maximums mass SMBHs) 
\item Is the physics of accretion redshift dependent (e.g. metals in the early Universe)?
\end{itemize}


\section*{Structure}
\begin{itemize}
\item What is the BLR?
\item What the actual frig is the Broad Line Region?
\item Are Warm Absorbers seen in X-rays due to a thermal wind from the torus? 
\item What is the NLR? 
\item How do we make a torus have large scale height?
\item Do all AGN have tori - Do true type 2 seyferts?
\item What geometry does the dust have? (oldie but a goodie)
\item Are any of Mrk 231, Mrk 1018, PDS 456 or NGC5548 actual “rosetta stones” for the general AGN population?
\item Do jets associated with radio-emission actually do anything connected to galaxy formation?
\end{itemize}


\section*{General galactic impacts}
\begin{itemize}
\item How do we resolve the paradox of rapid AGN evolution (e.g. in their luminosity function) and the fact they are being touted using several methods to be used as Standard(isable) Candles to high-$z$?

\item  Where are the $100 - 10,000 M_{\odot}$ IMBHs?
\end{itemize}

\end{document}