\documentclass[11pt]{article}
\setlength {\textwidth}{180mm} 
\setlength {\textheight}{260mm}
\topmargin=-35.00mm
\oddsidemargin=-10.00mm
\pagestyle{empty}

\input{format}

\begin{document}

\title{A Guide to DockerLiberty and the Pursuit of Happiness}
\author{Nicholas P. Ross}
\date{\today}
\maketitle


\begin{abstract}
This is a simple document which will give some overviews, NPR-style
notes and general things-to-remember for {\tt Docker}. Docker is an
open platform for developers and sysadmins to build, ship, and run
distributed applications, whether on laptops, data center VMs, or the
cloud.
\end{abstract}


%Section heading
\section{Docker}

Purpose: This document is a place where we/I (NPR) will keep notes on
how to use Docker \href{https://www.docker.com/}{\tt
(https://www.docker.com/}.\\

\noindent
``Docker is the world's leading software containerization platform''.\\

\noindent
``Docker containers wrap a piece of software in a complete filesystem that contains everything needed to run: code, runtime, system tools, system libraries – anything that can be installed on a server. This guarantees that the software will always run the same, regardless of its environment.''\\


Definition (from,of course Wikipedia): 
Docker is an open-source project that automates the deployment of applications inside software containers.  

Operating-system-level virtualization is a server virtualization method in which the kernel of an operating system allows the existence of multiple isolated user-spaceinstances, instead of just one. Such instances, which are sometimes called containers, software containers,[1] virtualization engines (VEs) or jails (FreeBSD jail or chroot jail), may look and feel like a real server from the point of view of its owners and users.

{\tt User\_space:} A modern computer operating system usually segregates virtual memory into kernel space and user space.[a] Primarily, this separation serves to provide memory protection and hardware protection from malicious or errant software behaviour.
Kernel space is strictly reserved for running a privileged operating system kernel, kernel extensions, and most device drivers. In contrast, user space is the memory area where application software and some drivers execute.

\newpage
\section{Glossary (from one of the Cheat Sheets)}

\begin{itemize}					
\item{Layer - a set of read-only les to provision the system.}
\item{Image - a read-only layer that is the base of your container. Might have a parent image.}
\item{Container - a runnable instance of the image.}
\item{Registry / Hub - central place where images live.}
\item{Docker machine - a VM to run Docker containers (Linux does this natively).}
\item{Docker compose - a utility to run multiple containers as a system.}
\end{itemize}					
			
		


Initial Download, installation and tests:

~> docker --version
Docker version 1.12.5, build 7392c3b
~> docker-compose --version
docker-compose version 1.9.0, build 2585387
~> docker-machine --version
docker-machine version 0.8.2, build e18a919
~> 


~ > docker ps  %Lists the running containers:
CONTAINER ID  IMAGE   COMMAND     CREATED  STATUS PORTS NAMES
fd68d79e8ad8  nginx   "nginx -g 'daemon off"   About a minute ago   Up About a minute   0.0.0.0:80->80/tcp, 443/tcp   webserver

~ > docker stop webserver 
webserver
~ > docker ps
CONTAINER ID        IMAGE               COMMAND             CREATED             STATUS              PORTS               NAMES
~ > docker ps
CONTAINER ID        IMAGE               COMMAND             CREATED             STATUS              PORTS               NAMES
~ > docker ps -a
CONTAINER ID        IMAGE               COMMAND                  CREATED             STATUS                         PORTS               NAMES
fd68d79e8ad8        nginx               "nginx -g 'daemon off"   3 hours ago         Exited (0) About an hour ago                       webserver
09ebf86dba83        hello-world         "/hello"                 3 hours ago         Exited (0) 3 hours ago                             drunk_colden
3a49afffde73        hello-world         "/hello"                 5 hours ago         Exited (0) 5 hours ago                             dreamy_swanson
1008b9c91a71        ubuntu              "bash"                   5 hours ago         Exited (0) 5 hours ago                             lonely_golick
9cbf9f6c9ec1        hello-world         "/hello"                 5 hours ago         Exited (0) 5 hours ago                             compassionate_thompson



> docker run -it -p 8889:8889 opennetworkinsight/oni-demo

> docker ps
CONTAINER ID        IMAGE                         COMMAND                  CREATED             STATUS              PORTS                    NAMES
b9bd7c28792f        opennetworkinsight/oni-demo   "/bin/sh -c /oni-o..."   11 seconds ago      Up 9 seconds        0.0.0.0:8889->8889/tcp   optimistic_feynman

> docker exec -it b9bd7c28792f /bin/bash


Docker Cheat Sheets

Docker_CheatSheet_08.09.2016_0.pdf
https://zeroturnaround.com/rebellabs/docker-commands-and-best-practices-cheat-sheet/
https://www.cheatography.com/aabs/cheat-sheets/docker-and-friends/

https://github.com/docker/docker/issues/3285



Other Docker links and resources

https://valdhaus.co/writings/docker-misconceptions/
https://developer.ibm.com/dwblog/2016/what-is-docker-containers/


https://docs.docker.com/engine/reference/run/
https://docs.docker.com/engine/reference/run/#/expose-incoming-ports



\end{document}

