\documentclass[11pt]{article}
%\setlength {\textwidth}{180mm} 
%\setlength {\textheight}{260mm}
%\topmargin=-35.00mm
%\oddsidemargin=-10.00mm
%\pagestyle{empty}


\input{format}

\begin{document}

\title{A Guide to Bayes}
\author{Nicholas P. Ross}
\date{\today}
\maketitle


\begin{abstract}
This is a simple document that discusses the basis and basics of Bayes. 
\end{abstract}


\tableofcontents


\newpage
\section{Bayes' Theorem}

Bayes' theorem is:

\begin{equation} 
P(A|B) = \frac{ P(B|A)  \:   P(A)}  {P(B)}
\end{equation}
where\\

\noindent
$P(A)$ and $P(B)$ are the probabilities of observing A and B without regard to each other.\\

\noindent
$P(A | B)$, a conditional probability, {\it is the probability of observing event A given that B is true.}\\

\noindent
$P(B | A)$ is the probability {\it of observing event B given that A is true}.\\




\newpage
\section{Bayesian inference}

Bayesian inference derives the posterior probability as a consequence
of two antecedents, a prior probability and a ``likelihood function''
derived from a statistical model for the observed data. Bayesian
inference computes the posterior probability according to Bayes'
theorem:

\begin{equation} 
P(H|E) = \frac{ P(E|H)  \:   P(H)}  {P(E)}
\end{equation}
where:\\

\noindent
$|$ denotes a conditional probability; more specifically, it means
``given''.\\

\noindent
$H$ stands for any hypothesis whose probability may be affected by
data (called evidence below). Often there are competing hypotheses,
from which one chooses the most probable.\\

\noindent
the evidence $E$ corresponds to new data that were not used in
computing the prior probability.\\

\noindent
$P(H)$, the prior probability, is the probability of $H$ before $E$ is
observed. This indicates one's previous estimate of the probability
that a hypothesis is true, before gaining the current evidence.\\

\noindent
$P(H | E)$ the posterior probability, is the probability of $H$ given
$E$, i.e., after $E$ is observed. This tells us what we want to know:
the probability of a hypothesis given the observed evidence.\\

\noindent
$P (E | H)$ is the probability of observing $E$ given $H$. As a
function of $E$ with $H$ fixed, this is the likelihood. The likelihood
function should {\bf not} be confused with $P(H | E)$ as a function of 
$H$ rather than of $E$. It indicates the compatibility of the evidence with the given
hypothesis.\\

\noindent
$P(E)$ is sometimes termed the marginal likelihood or ``model
evidence''. This factor is the same for all possible hypotheses being
considered. (This can be seen by the fact that the hypothesis $H$ does
not appear anywhere in the symbol, unlike for all the other factors.)
This means that this factor does not enter into determining the
relative probabilities of different hypotheses. \\

%Note that, for different values of {\displaystyle \textstyle H} \textstyle H, only the factors {\displaystyle \textstyle P(H)} \textstyle P(H) and {\displaystyle \textstyle P(E\mid H)} \textstyle P(E\mid H) affect the value of {\displaystyle \textstyle P(H\mid E)} \textstyle P(H\mid E). As both of these factors appear in the numerator, the posterior probability is proportional to both. In words:

%(more precisely) The posterior probability of a hypothesis is determined by a combination of the inherent likeliness of a hypothesis (the prior) and the compatibility of the observed evidence with the hypothesis (the likelihood).

%(more concisely) Posterior is proportional to likelihood times prior.

\noindent
Note that Bayes' rule can also be written as follows:
\begin{equation}
P(H\mid E)={\frac {P(E\mid H)}{P(E)}}\cdot P(H)
\end{equation}
where the factor $\frac {P(E\mid H)}{P(E)}$ represents the impact of
$E$ on the probability of $H$.









\newpage
\section{References}
\href{https://en.wikipedia.org/wiki/Bayesian\_inference}{https://en.wikipedia.org/wiki/Bayesian\_inference}\\
\href{hrefhttps://en.wikipedia.org/wiki/Bayes\%27\_theorem}{https://en.wikipedia.org/wiki/Bayes\%27\_theorem}\\

\citet{Croom04}

\bibliographystyle{mn2e}
\bibliography{/cos_pc19a_npr/LaTeX/tester_mnras}

\end{document}

